Fast inhibitory loop explains functional map development with short-range inhibition.

### 2017-01-11 paper.tex
dsa

Competition between populations of neurons has been proposed as one of the canonical computations of cortical 
networks, and has been hypothesized to underly range of brain functions including working memory \citep{Amit1995,Durstewitz2000},
orientation tuning \citep{Somers1995,Ben-Yishai1995}, and functional map development \citep{VonderMalsburg1973,CMVC,Antolik2011}.
In developmental models of functional cortical organization the competition occurs between populations of neurons spatially offset 
along the cortical surface, whereby local populations mutually reinforce each other via excitatory connections (short-range 
excitation) while long-range inhibition facilitates competition between the local populations and stabilizes the activity in the 
network. Such so called Mexican-hat arrangement of recurrent interactions, however, is in stark contrast to the know anatomical arrangement
of cortical circuitry: the excitatory neurons (especially in superficial layers) tend to form long-range arborizations spanning 
multiple columns while the axons of majority of inhibitory neurons are confined to area only several hundreds of micrometers 
in diameter \citep{Buzas2006,Budd2001}.

>>>>

Competition between populations of neurons has been proposed as one of the canonical computations of cortical 
networks, and has been hypothesized to underly range of brain functions including working memory \citep{Amit1995,Durstewitz2000,Deco2003},
attention \citep{Deco2003}, orientation tuning \citep{Somers1995,Ben-Yishai1995,Antolik2011}, and functional map development \citep{VonderMalsburg1973,CMVC,Antolik2011}. In developmental models of functional cortical organization the competition occurs between populations of neurons spatially offset 
along the cortical surface, whereby local populations mutually reinforce each other via excitatory connections (short-range 
excitation) while long-range inhibition facilitates competition between the local populations and stabilizes the activity in the 
network. Such so called Mexican-hat arrangement of recurrent interactions, however, is in stark contrast to the know anatomical arrangement
of cortical circuitry: the excitatory neurons (especially in superficial layers) tend to form long-range arborizations spanning 
multiple columns while the axons of majority of inhibitory neurons are confined to area only several hundreds of micrometers 
in diameter \citep{Buzas2006,Budd2001}.
